Defocus Corrected Large Area Cryo-EM (DeCo-LACE) for Label-Free Detection of Molecules across Entire Cell Sections

### 2022-05-20 manuscript.tex
custom deploy [ci skip]
This build is based on
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/6a99bb6d7d1ae0bbee70874ab4b79ba22f7fe1ce.

This commit was created by the following CI build and job:
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/commit/6a99bb6d7d1ae0bbee70874ab4b79ba22f7fe1ce/checks
https://github.com/jojoelfe/deco_lace_template_matching_manuscript/actions/runs/2355345427

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/9e84ed3862d1eaba8f35e633a0051d4314907579/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/9e84ed3862d1eaba8f35e633a0051d4314907579}{jojoelfe/deco\_lace\_template\_matching\_manuscript@9e84ed3}
on May 19, 2022.

>>>>

This manuscript
(\href{https://jojoelfe.github.io/deco_lace_template_matching_manuscript/v/6a99bb6d7d1ae0bbee70874ab4b79ba22f7fe1ce/}{permalink})
was automatically generated
from \href{https://github.com/jojoelfe/deco_lace_template_matching_manuscript/tree/6a99bb6d7d1ae0bbee70874ab4b79ba22f7fe1ce}{jojoelfe/deco\_lace\_template\_matching\_manuscript@6a99bb6}
on May 20, 2022.
